Supplementary Materials

### 2018-03-30 paper/appendix_modelDescription.tex
minor change in appendix

where G is the aggregation layer (e.g. two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation. With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict weight on each entailment score:
\begin{align}
  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
\end{align}

>>>>

where G is the aggregation layer (e.g. two-layer ReLU) and $[\cdot|\cdot]$ denotes concatenation. With the aggregated premise feature $\boldsymbol{u}_i$ and hypothesis feature $\boldsymbol{v}_j$, the classifier does further feature conjunction to predict score on each entailment label:
\begin{align}
  \boldsymbol{y} &= Z([\sum_i \boldsymbol{u}_i | \sum_j \boldsymbol{v}_j]) \label{eq:yscore}
\end{align}
